Sushi monster

### 2025-02-21 inst/jss_hyper3_real.Rnw
make sushi a package dataset

% -*- mode: noweb; noweb-default-code-mode: R-mode; -*-
\documentclass[article]{jss}
\usepackage{booktabs}
\usepackage{units}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}

@@

@@

<<defcalculate_sushi_H>>=

ec <- c("ebi"  = 1, "anago" = 2, "maguro" = 1, "ika" = 1, "uni" = 1,
        "sake" = 1, "tamago" = 1, "toro" = 2, "tekka-maki" = 2,
        "kappa-maki" = 1)

make_sushi_H <- function(lambda){    
    for(i in seq_len(nrow(a))){
        H <- H + cheering3(sushi_types[a[i,]], e=ec, h=c(1, lambda))
    }
    return(H)
}
@

<<calclikesushi, cache=TRUE>>=
f <- function(lambda){
   H <- make_sushi_H(a, lambda=lambda)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=4,len=5)
L <- sapply(s,f)
@

>>>>

% -*- mode: noweb; noweb-default-code-mode: R-mode; -*-
\documentclass[article]{jss}
\usepackage{booktabs}
\usepackage{units}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}

@@

\begin{wrapfigure}{r}{0.1\textwidth}
    \centering
    \includegraphics[width=0.1\textwidth]{hyper2.png}\\
\end{wrapfigure}

@@

Implementation in \code{hyper3} formalism is straightforward.  Object
\code{sushi\_eq\_class} specifies the two equivalence classes

<<show_sushi_eq_classes>>=
sushi_eq_classes
head(noquote(sushi_table))
@

We can now use this to define a bespoke likelihood function, using
$\lambda$ as  the argument:

<<defcalculate_sushi_H>>=
make_sushi_H <- function(lambda){
    H <- hyper3()
    for(i in seq_len(nrow(sushi_table))){
        H <- H + cheering3(sushi_table[i,], e=sushi_eq_classes, h=c(1, lambda))
    }
    return(H)
}
@

Then, as before, we may define a profile likelihood function of $\lambda$:

<<calclikesushi, cache=TRUE>>=
f <- function(lambda){
   H <- make_sushi_H(lambda)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=3,len=2)
L <- sapply(s,f)
@

### 2025-02-21 inst/sushi.Rmd
make sushi a package dataset

```{r}
sushi_types <- c("ebi", "anago", "maguro", "ika", "uni", "sake", "tamago", "toro", "tekka", "kappa")
a[] <- sushi_types[a]
noquote(a)
    ec <- c("ebi"  = 1, "anago" = 2, "maguro" = 1, "ika" = 1, "uni" = 1,
          "sake" = 1, "tamago" = 1, "toro" = 2, "tekka" = 2,
          "kappa" = 1)

```

@@

    for(i in seq_len(nrow(a))){
        H <- H + cheering3(a[i,], e=ec, h=c(1,lambda))
    }
    return(H)
}
```

@@

```{r,label=savesushidataset}
sushi_table <- a
save(sushi_table,  sushi, sushi_maxp, file="sushi.rda")
```

>>>>

```{r}
sushi_types <- c("ebi", "anago", "maguro", "ika", "uni", "sake", "tamago", "toro", "tekka", "kappa")
a[] <- sushi_types[a]
noquote(a)
sushi_eq_classes <-
    c("ebi"  = 1, "anago" = 2, "maguro" = 1, "ika" = 1, "uni" = 1,
      "sake" = 1, "tamago" = 1, "toro" = 2, "tekka" = 2,
      "kappa" = 1)
```

@@

    for(i in seq_len(nrow(a))){
        H <- H + cheering3(a[i,], e=sushi_eq_classes, h=c(1,lambda))
    }
    return(H)
}
```

@@

```{r,label=savesushidataset}
sushi_table <- a
save(sushi_table,  sushi, sushi_maxp, sushi_eq_classes, file="sushi.rda")
```
